### 2025-11-11 cluster-analysis.qmd
20251111 - model fit criteria

There are several model fit criteria we can use to identify the optimal number of tiers in terms of the tradeoff between fit and parsimony.
For the Bayesian Information Criterion (BIC), closer to zero is better.
For the Integrated Complete-data Likelihood (ICL), higher is better.
For the bootstrapped likelihood ratio tests, a significant likelihood ratio test indicates that the model with more clusters fits significantly better than the model with fewer clusters.

>>>>

There are several model fit criteria we can use to identify the optimal number of clusters in terms of the tradeoff between fit and parsimony.
For the Bayesian Information Criterion (BIC), closer to zero is better.
For the Integrated Complete-data Likelihood (ICL), higher is better.
For the bootstrapped likelihood ratio tests, a significant likelihood ratio test indicates that the model with more clusters fits significantly better than the model with fewer clusters.
Although the model fit criteria can be helpful for identifying the optimal number of clusters, they should only be used as a guide.
Ultimately, cluster analysis is only useful to the extent that the clusters and useful and interpretable, which may mean selecting more (or fewer) clusters than are suggested by the model fit criteria.
